SunPy - Python for Solar Physics

### 2014-01-30 1-Introduction.tex
small tweaks to intro

Science is driven by the analysis of data of growing variety and complexity.
Modern advances in sensor
technology, combined with the availability of inexpensive storage, has led to
rapid increases in the sheer amount of data available to scientists in almost
every discipline.  Solar physics is no exception to this trend. For example,
NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched in February 2010,
produces over 1 TB of catalogued and stored data per day \citep{aia}. Managing and
analysing this mountain of data
requires increasingly sophisticated software tools.
These tools should be robust, be easy of use and modify, have a
transparent development history, and conform
to standards.  Software with these qualities provide a strong
foundation and can support the needs of the community as data
volumes grow and science questions evolve.
%schriste - the opening paragraph still needs work
%ji - I had a go.
%schriste - looks good, made a small fix

@@

The purpose of this paper is to provide an overview of SunPy's current 
capabilities, an overview of the project's development model, community aspects of the 
SunPy project, and future plans for the project. The latest release of SunPy, version 0.4,
can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be
installed using the \href{http://pypi.python.org/pypi}{Python package index}.

>>>>

Science is driven by the analysis of data of growing variety and complexity.
Modern advances in sensor
technology, combined with the availability of inexpensive storage, has led to
rapid increases in the amount of data available to scientists in almost
every discipline.  Solar physics is no exception to this trend. For example,
NASA's \textit{Solar Dynamics Observatory} (\textit{SDO}) spacecraft, launched in February 2010,
produces over 1 TB of data per day \citep{aia}. Managing and
analysing this mountain of data
requires increasingly sophisticated software tools.
These tools should be robust, easy of use and modify, have a
transparent development history, and conform
to modern software engineering standards.  Software with these qualities provide a strong
foundation and can support the needs of the community as data
volumes grow and science questions evolve.

@@

The purpose of this paper is to provide an overview of SunPy's current 
capabilities, an overview of the project's development model, community aspects of the 
project, and future plans. The latest release of SunPy, version 0.4,
can be downloaded from \href{http://sunpy.org}{www.sunpy.org} or can be
installed using the \href{http://pypi.python.org/pypi}{Python package index}.
